---
title: "10-import"
output: html_notebook
---

# Goal

We want to predict the quantity of the items sold per branch in each day. 

*hint: If you want to see more information of the dataset, please go to README2.*


# Read in and check the data

a. load libraries
```{r load library}
library(readr)
library(tidyverse)
library(lubridate) # date
library(janitor) # clean_names
library(assertr) # assert
```


b. import dataset

```{r import data}
supermarket <- read_csv("supermarket_sales.csv")
```


c. clean names

we use `clean_names()` to clean the volumn names.

```{r clean_names}
supermarket <- clean_names(supermarket)
names(supermarket)
```


d. dimension and the structures

Checking the structures of the data, we find that the dataset has 1000 observations and 17 attributes.
```{r Check the dimensions and the structures}
dim(supermarket)
str(supermarket)
```


e. check NA

```{r Check NA}
supermarket %>% 
  verify(not_na(.))

```
There is no NA in the dataset.


f. Assert 

Before we start doing data exploration and feature engineering, we need to check whether there exists abnormal values in each variable. Thus we use `assert()` function to detect the abnormalities.

(1)  We want to check whether invoice_id is unique. The result shows that it is.
```{r assert id}
supermarket %>%
  assert(is_uniq, invoice_id)
```


(2) We want to check the following categorical variables.
```{r assert categorical variables}
supermarket %>%
  assert(in_set("A", "B", "C"), branch) %>%  # check whether the dataset contains only three branch
  assert(in_set("Female", "Male"), gender) %>%  # check whether the gender only include male and female
  assert(in_set("Ewallet", "Cash", "Credit card"), payment) # check whether there are more than three types of payment methods which are listed above
```
The dataset looks good!


(3) we want to check the following numerical variables to see if they are in the prospected ranges.
```{r assert numerical variables}
supermarket %>%
  assert(within_bounds(1, 10), rating) %>%  # check the ratings that is assumed to be in 1 to 10.
  assert(within_bounds(0, max(supermarket$unit_price)), unit_price) %>%  # check the unit_price to see whether it is larger than 0.
  assert(within_bounds(0, 100), gross_margin_percentage) # check the gross_margin_percentage to see whether it ranges from 0 to 100.
```

The results show that there is no abnormal value in the dataset.


# Clean up the data

After checking the data, we found that the dataset is almost clean. Now we can do some changes for the type of the variables.

For "date" variable, we know that it is supposed to be Date type instead of char. So we use `mdy()` to make this change.

```{r change the types of date variables}
supermarket$date <- mdy(supermarket$date)
str(supermarket$date)
```

I think the customer type is a good predictor, but naming the values into "0" and "1" will be better for modelling. Thus, I will recode the value for this variable, "1" equals to "Member" and "0" equals to "Normal".

```{r}
supermarket %>%
  mutate(customer_type = ifelse(customer_type == "Member", 1, 0))
```

Now the data looks more clean. Now we can start playing with data!
